MTB Expression Analysis

### 2018-01-12 analysis/MTB_Expression_Analysis.Rmd
wflow_publish("MTB_Expression_Analysis.Rmd")

For each bacterial infection at certain timepoint, we have six controls and six treatments, denoted as $X_1,X_2,X_3,X_4,X_5,X_6$ and $Y_1,Y_2,Y_3,Y_4,Y_5,Y_6$. Then the estimated effect size and variance are defined below:
$$
\hat\beta = \bar Y-\bar X; \\
\hat s = \sqrt{\hat\sigma_x^2/6+\hat\sigma_y^2/6.}
$$
Here $\bar X$, $\bar Y$ are sample means, and $\hat\sigma_x$, $\hat\sigma_y$ are sample 
variances.

@@

```{r}
source('../code/function.R')
betahat = read.table("../data/betahat.txt", header = TRUE, sep = "\t",
               stringsAsFactors = FALSE)
sebetahat = read.table("../data/sebetahat.txt", header = TRUE, sep = "\t",
               stringsAsFactors = FALSE)
z18_k5 = generic.cormotif(betahat[,9:16],sebetahat[,9:16],K=5,mess=FALSE)
plotMotif(z18_k5$bestmotif)
```

@@

```{r}
dat_cpm <- read.table("../data/table-s1.txt", header = TRUE, sep = "\t",
                      stringsAsFactors = FALSE)
# The first two columns are gene information
rownames(dat_cpm) <- dat_cpm$id
gene_names <- dat_cpm$name
names(gene_names) <- dat_cpm$id

id = rownames(dat_cpm)
lfsr18 = z18_k5$lfsr[[1]][,1] 
list = id[lfsr18<0.01]
a = intersect(S3[,2],list)
print(gene_names[a])
```

>>>>

For each bacterial infection at certain timepoint, we have six controls and six treatments, denoted as $X_1,X_2,X_3,X_4,X_5,X_6$ and $Y_1,Y_2,Y_3,Y_4,Y_5,Y_6$. Then the estimated effect size and standard error are defined below:
$$
\hat\beta = \bar Y-\bar X; \\
\hat s = \sqrt{\hat\sigma_x^2/6+\hat\sigma_y^2/6.}
$$
Here $\bar X$, $\bar Y$ are sample means, and $\hat\sigma_x$, $\hat\sigma_y$ are sample 
variances. Then we have
$$
\hat\beta|\hat s\sim N(\beta,\hat s^2).
$$

@@

```{r,cache=TRUE}
source('../code/function.R')
betahat = read.table("../data/betahat.txt", header = TRUE, sep = "\t",
               stringsAsFactors = FALSE)
sebetahat = read.table("../data/sebetahat.txt", header = TRUE, sep = "\t",
               stringsAsFactors = FALSE)
z18_k5 = generic.cormotif(betahat[,9:16],sebetahat[,9:16],K=5,mess=FALSE)
plotMotif(z18_k5$bestmotif)
```

@@

```{r}
dat_cpm <- read.table("../data/table-s1.txt", header = TRUE, sep = "\t",
                      stringsAsFactors = FALSE)
# The first two columns are gene information
gene_names <- dat_cpm$name
names(gene_names) <- dat_cpm$id

S3 = read.csv("../data/S3.csv",
              header = FALSE,stringsAsFactors = FALSE)
id = rownames(dat_cpm)
lfsr18 = z18_k5$lfsr[[1]][,1] 
list = id[lfsr18<0.01]
a = intersect(S3[,2],list)
print(gene_names[a])
```
